### 2021-06-03 paper/introduction.tex
Line breaks.
Correct some model features and typos.

    \item We distinguish detected and undetected cases. The share of detected cases varies over time and across age groups. Moreover, it can be influenced by rapid testing policies.
    \item High quality Python code for the model is freely available on Github, well
          documented and very flexible\footnotemark. We are actively looking for
          researchers who want to use our model for their projects and apply it to other
          contexts.
\end{enumerate}

\footnotetext{
    The code can be found under \url{https://github.com/covid-19-impact-lab/sid} and the
    documentation with tutorials and background information under
    \url{https://sid-dev.readthedocs.io/}.
}

The model achieves a good fit on German data of infection and fatality rates, even though most parameters are calibrated from the literature and observable datasets and only a few parameters are estimated inside the model. At accurately predicts the rise of the B117 mutation in spring 2020. It can also explain the surprising decline of case numbers at the end of April, without making ad hoc assumptions on behavioral changes at the time.

>>>>

    \item We distinguish detected and undetected cases. The share of detected cases
          varies over time and across age groups. Moreover, it can be influenced by rapid
          testing policies.

    \item High quality Python code for the model is freely available on Github, well
          documented and very flexible\footnotemark.
\end{enumerate}

\footnotetext{
    The code can be found at \url{https://github.com/covid-19-impact-lab/sid} and the
    documentation with tutorials and background information at
    \url{https://sid-dev.readthedocs.io/}.
}

The model achieves a good fit on German data of infection and fatality rates, even
though most parameters are calibrated from the literature and observable datasets and
only a few parameters are estimated inside the model. It accurately predicts the rise of
the B117 mutation in spring 2020. It can also explain the surprising decline of case
numbers at the end of April, without making ad hoc assumptions on behavioral changes at
the time.

### 2021-06-03 paper/report.tex
Correct some model features and typos.

\paragraph{Further important features }
\begin{itemize}
    \item Vaccinations including remaining infectiousness
    \item Tests including false positives / negatives
    \item Various strains
    \item Progression of CoViD-19 and infectiousness
    \item Detailed schooling models (A/B classes, full closures, hygiene multipliers,...)
    \item Detailed work models (work from home)
    \item Model for undetected infections to make publicly disclosed data usable (only thing that requires bespoke tailoring for other countries?)
\end{itemize}

>>>>

\paragraph{Further important features }
\begin{itemize}
    \item Vaccinations including vaccination priority according to age and systemic relevance of work
    \item Tests including false positives / negatives
    \item Various strains
    \item Age dependent susceptibility and progression of CoViD-19
    \item Detailed schooling models (A/B classes, full closures, hygiene multipliers,...)
    \item Detailed work models (work from home, work contact priority, daily, weekly and non-recurrent work contacts)
    \item Model for undetected infections to make publicly disclosed data usable (only thing that requires bespoke tailoring for other countries?)
\end{itemize}
